### 2020-03-11 tex/intro.tex
Small corrections and initial additional thoughts

Currently, the inflation rewards are computed for each Ursula based on the number of 
active policies it holds conditioned on being online during the period of each of these 
policies. Confirming the status of being online is done by having each Ursula call a 
simple function in one of the NuCypher contracts to signal that she is around.

Same for the fees, Ursula will collect some of the Ether locked by Alice at the end 
of the policy duration given that this Ursula stays online for the whole duration. 
Again, the latter is tracked by watching the confirm activity function calls Ursula 
make during the policy period.

@@

\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
an stay offline offline, not answering any Bob, and be online just to call the confirm activity 
function. This allows Ursula to collect both inflation rewards 
and fees without doing anything, and even worse, it will be able to get her stake back at 
the end of a policy duration.
\end{itemize}

@@

Although we can use the number of served requests to compute the inflation 
rewards as well, this will encourage Ursula to collude with Bob to issue large 
number of requests. Even it may encourage Ursula to deploy its own Alice(s) 
and Bob(s) to increase the demand, and thus, the cut of the inflation rewards.

>>>>

Currently, the inflation rewards are computed for each Ursula based on the size of their stake, and their confirmation that they are online, once per period. Confirming the status of being online is done by having each Ursula call a 
simple function in one of the NuCypher contracts to signal that she is around.

As for fees, Ursula collects the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed their online status.

@@

\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
can stay offline, not answering any Bob, and be online just to call the confirm activity 
function. This allows Ursula to collect both inflation rewards 
and fees without doing anything, and even worse, it will be able to get her stake back once it unlocks (policies being managed by Ursula will have expired by this point). 
\end{itemize}

@@

Although we can use the number of served requests to compute the inflation 
rewards as well, this will encourage Ursula to collude with Bob to issue large 
number of requests. If inflation rewards were to be distributed based on the earning of fees (which is desirable, as it would link node subsidization more closely with the network service), this might encourage Ursula to deploy its own Alice(s) 
and Bob(s) to increase the demand, and thus, the cut of the inflation rewards.

### 2020-03-11 tex/solutions.tex
Small corrections and initial additional thoughts

Thus, in this setup, there is only one computation party, or prover, namely, Ursula. 
For each round, where a round could be the time needed to mine a block on the 
blockchain, Ursula starts with an input $x_1$, which is a signed and fresh request 
from Bob. It answers this request with $cFarg_{x_1}$ and produces a correctness 
proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, 
which is the input for the next step in the computation, Ursula answers 
this request as before and produces $cFarg_{x_2}$ and a correctness proof $\pi_2$, then 
it uses $(x_2, cFarg_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
$\hat{\pi}_2$ does not only 
attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served 
two valid distinct requests until now. The same process is repeated until the end of the 
round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of 
served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
this process pictorially.

@@

\item Verify the correctness of each $cFarg$ as in the Umbral 
scheme.

@@

\subsubsection{On the committee election.} This can be done 
by using some deterministic computation over a block hash and mapping 
the output to Ursulas' public keys. So the selection is not in the hand of the 
working Ursula to prevent any potential collusion.

The above scheme works under the assumption that at least one Ursula 
in the elected committee is honest, which pertains to an assumption on the 
least number of honest Ursulas in the network.

@@

To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
This can be done by having the policy contract select at random (like based 
on the block hash or any other mechanism) the leave IDs to be opened. If 
Ursula fails to open them correctly within a predefined timeframe, she loses the 
whole feed she was supposed to collect for serving $\omega$ requests.

An alternative approach to the challenge/open scheme described above is to 
have Ursula publish the full Merkle tree on, e.g., some known public space, but 
not on the blockchain. Make the full record available online for a specific period 
to allow anyone to verify the work. If no one file a complaint about the tree (we 
still need to define correctness properties, like checking all Bob public keys are 
defined in the policy created by Alice, and that the response is valid by checking the 
proof produced by Umbral), Ursula collects the fees of the service. On the other 
hand, a valid complaint or proof-of-cheating costs Ursula the full amount of fees.

>>>>

Thus, in this setup, there is only one computation party, or prover, namely, Ursula. 
For each round, where a round could be the time needed to mine a block on the 
blockchain, Ursula starts with an input $x_1$, which is a signed and fresh request 
from Bob. It answers this request with $cFrag_{x_1}$ and produces a correctness 
proof $\pi_1$ as defined in the Umbral scheme, in addition to another correctness 
proof $\hat{\pi}_1$ that will be used in the PCD composition. Then, when the next request $x_2$ arrives, 
which is the input for the next step in the computation, Ursula answers 
this request as before and produces $cFrag_{x_2}$ and a correctness proof $\pi_2$, then 
it uses $(x_2, cFrag_{x_2}, \pi_2)$ and the previous proof $\hat{\pi}_1$ to produce $\hat{\pi}_2$. 
$\hat{\pi}_2$ does not only 
attest to the correctness of $cFrag_{x_2}$, but also attests to the fact that Ursula has served 
two valid distinct requests until now. The same process is repeated until the end of the 
round to produce a single proof $\hat{\pi}_{\omega}$ along with the number of 
served requests $\omega$. Figure~\ref{pcd-based-sol} depicts 
this process pictorially.

@@

\item Verify the correctness of each $cFrag$ as in the Umbral 
scheme.

@@

\subsubsection{On the committee election.} This can be done 
by using some deterministic computation over a block hash and mapping 
the output to Ursulas' public keys. So the selection is not in the hand of the 
working Ursula to prevent any potential collusion. The selection may also take into account the presence and size of each Ursula's stake, to avoid an attacker spinning up enormous numbers of Ursulas in order to increase the chance they control the entire committee.

The above scheme works under the assumption that at least one Ursula 
in the elected committee is honest, which pertains to an assumption on the 
least number of honest Ursulas in the network. If the latter assumption is under threat, one mitigating approach is to increase $t$ (the committee size).

@@

To prove correctness, Ursula will be challenged to open some leaves in the Merkle tree. 
This can be done by having the policy contract select at random (like based 
on the block hash or any other mechanism) the leaf IDs to be opened. If 
Ursula fails to open them correctly within a predefined timeframe, she loses the 
whole feed she was supposed to collect for serving $\omega$ requests.

An alternative approach to the challenge/open scheme described above is to 
have Ursula publish the full Merkle tree on, e.g., some known public space, but 
not on the blockchain. Make the full record available online for a specific period 
to allow anyone to verify the work. If no one file a complaint about the tree (we 
still need to define correctness properties, like checking all Bob public keys are 
defined in the policy created by Alice, and that the response is valid by checking the 
proof produced by Umbral), Ursula collects the fees of the service. On the other 
hand, a valid complaint or proof-of-cheating costs Ursula the full amount of fees, or potentially involves slashing her stake.
